Robust co-occurrence quantification for low-dimensional lexical distributional semantics

### 2016-02-29 figures/best.tex
Figure merge

\begin{figure*}
  \centering
  \begin{subfigure}[b]{\textwidth}
    \centerline{\includegraphics[width=1.1\textwidth]{supplement/figures/SimLex999-best}}
    \caption{\textbf{SimLex-999.} The black line refers to the score of 0.393.
      This work: 0.385,
      SGNS: 0.438,
      GloVe: 0.398.
    }
    \label{fig:simlex-ppmi-best-simlex}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \centerline{\includegraphics[width=1.1\textwidth]{supplement/figures/men-best}}
    \caption{\textbf{MEN.} The black line refers to the score of 0.745.
      This work: 0.765,
      SGNS: 0.774,
      GloVe: 0.729.
    }
    \label{fig:simlex-ppmi-best-men}
  \end{subfigure}

  \caption{\textbf{SPMI best configurations.} Black line shows the best count models reported by \protect\newcite{TACL570}. We also give our best score, SGNS and GloVe numbers from that study for comparison.}
  \label{fig:simlex-ppmi-best}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \begin{subfigure}[t]{0.6\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-best}
    \caption{\textbf{SimLex-999.} The black line refers to the score of 0.393. \\
      This work: 0.385,
      SGNS: 0.438,
      GloVe: 0.398.
    }
    \label{fig:best-simlex}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.37\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-global-best}
    \caption{\textbf{SimLex-999.}
    }
    \label{fig:global-best-simlex}
  \end{subfigure}

  \begin{subfigure}[t]{0.6\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/men-best}
    \caption{\textbf{MEN.} The black line refers to the score of 0.745. \\
      This work: 0.765,
      SGNS: 0.774,
      GloVe: 0.729.
    }
    \label{fig:best-men}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.37\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/men-global-best}
    \caption{\textbf{MEN.}
    }
    \label{fig:global-best-men}
  \end{subfigure}

  \caption{\textbf{Best configurations.} Black line shows the best count models reported by \protect\newcite{TACL570}. We also give our best score, SGNS and GloVe numbers from that study for comparison.}
  \label{fig:best}
\end{figure*}

### 2016-02-29 paper.tex
Figure merge

We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:simlex-ppmi-best-simlex}).

@@

Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}). Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.

>>>>

We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:best-simlex}).

@@

Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:best-men}). Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.
